Basic inferential data analysis.
========================================================
### Analyze the ToothGrowth data in the R datasets package
### 1. Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r setoptions, echo=FALSE}
opts_chunk$set(echo = FALSE, result = "hide")
```
- initial understanding of the data.(using facets)
- make boxplots to campare Tooth length with different dosage for each supplements
```{r boxplot, fig.height=2.5}
library(datasets)
library(ggplot2)
p <- ggplot(ToothGrowth, aes(factor(dose), len))
p+geom_boxplot()+facet_grid(.~supp)+labs(title = "plot1")
```
- make boxplot to compare Tooth length with different supplement for each dosage
```{r boxplot2, fig.height=2.5}
q <- ggplot(ToothGrowth, aes(factor(supp), len))
q +geom_boxplot()+facet_grid(.~dose)+labs(title = "plot2")
```
- from plot1 we can see the tooth length increase along with the increase of the dosage nomatter for which supplement.
- from plot2 it is a little hard to tell wheather there is difference impact on the tooth length between VC an OJ supplements for each dosage. (can make analysis on this point later)

### 2.Provide a basic summary of the data.
- Calculate the mean & sd for each dosage and supplement (use the ddply) 
```{r}
library(plyr)
TG_summary <- ddply(ToothGrowth,.(dose, supp), summarize, mean = mean(len), sd = sd(len))
as.factor(TG_summary$dose)
TG_summary
```

### 3.Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. 
- We have two type of supp: orange juice and vitamin C. We need to use hypothesis testing to make conclusion if both supp have the same impact on tooth length.
- use paired t-test to comapre mean for two supp for each dose
- the confidence interval is for the difference between the length of toothlength under the effect of OJ and VC for each dose.
```{r, echo=TRUE}
ToothGrowth <- transform(ToothGrowth, dose=as.factor(dose))
s <- split(ToothGrowth, list(ToothGrowth$supp, ToothGrowth$dose))
t1 <- t.test(s[[1]][[1]], s[[2]][[1]], paired = TRUE, alternative = "greater")#dose= 0.5
t2 <- t.test(s[[3]][[1]], s[[4]][[1]], paired = TRUE, alternative = "greater")#dose = 1
t3 <- t.test(s[[5]][[1]], s[[6]][[1]], paired = TRUE, alternative = "greater")#dose = 2
```
- the confidence level for dose 0.5 is `r t1$con`, and the p-value is `r t1$p.value`
- the confidence level for dose 0.5 is `r t2$con`, and the p-value is `r t2$p.value`
- the confidence level for dose 0.5 is `r t3$con`, and the p-value is `r t3$p.value`

### 4.State your conclusions and the assumptions needed for your conclusions. 
### assumptions:
- the hypothesis is: both supp have the same impact on tooth length.
- the alternative hypothesis is: OJ can promote the growth of toothlength than VC.
- significance level: 0.05

### conclusions: 
- OJ have more impact on the growth of toothlength under dose equals to 0.5 or 1.But can't get this conclusion when dose equals to 2. We need further research.